---
title: "interaction"
output: html_document
date: "2023-04-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Formalization

* How to interpret coefficients when you have an interaction term and you also
normalize some explanatory variables?

* Original model
$$
y_i = \beta_0 + \beta_1 d_i + \beta_2 w_i + \beta_3 d_i w_i + e_i
$$

* Model with normalized $W_i$: 

\begin{align*}
& y_i = \gamma_0 + \gamma_1 d_i + \gamma_2 z_i + \gamma_3 d_i z_i + \epsilon_i \\
& z_i = \frac{w_i - \overline{w_i}}{sd(w_i)}
\end{align*}

* Derivation:

\begin{align*}
y_i &= \gamma_0 + \gamma_1 d_i + \gamma_2 z_i + \gamma_3 d_i z_i + \epsilon_i\\
&= \gamma_0 + \gamma_1 d_i + \gamma_2 \frac{w_i - \overline{w_i}}{sd(w_i)} + 
\gamma_3 d_i \frac{w_i - \overline{w_i}}{sd(w_i)} + \epsilon_i\\
&= \gamma_0 - \frac{\gamma_2 \overline{w_i}}{sd(w_i)} +
\gamma_1 d_i - \frac{\gamma_3 \overline{w_i}}{sd(w_i)} d_i + 
\frac{\gamma_2}{sd(w_i)} w_i + \frac{\gamma_3}{sd(w_i)} d_i w_i + \epsilon_i\\
\end{align*}

* Correspondence:

$$
\beta_0 = \gamma_0 - \frac{\gamma_2 \overline{w_i}}{sd(w_i)}, \;\;
\beta_1 = \gamma_1 - \frac{\gamma_3 \overline{w_i}}{sd(w_i)}, \;\;
\beta_2 = \frac{\gamma_2}{sd(w_i)}, \;\; beta_3 = \frac{\gamma_3}{sd(w_i)}
$$



# Example

```{r, file = "interaction.R"}
# source("interaction.R", local = knitr::knit_global())
# or sys.source("your-script.R", envir = knitr::knit_global())
```
