---
title: '10, '
output: html_document
---

```{r, message=FALSE}
library(tidyverse)
```


# 10 Tibble
```{r}
# create tibble
tibble(
  x = 1:5,
  y = 1,
  z = x^2 + y
)
```

## the column name is flexible
```{r}
tb <- tibble(
  `:)` = "smile",
  ` ` = "space",
  `2000` = "number"
)
print(tb)

df <- data.frame(
  ":)" = "smile",
  " " = "space",
  "2000" = "number"
)
# see the difference between tb and df
print(df)

```

```{r}
tribble(
  ~x, ~y, ~z, # you need `~`
  #--|--|----
  "a", 2, 3.6,
  "b", 1, 8.5
)
```

## choose the element in tibble
```{r}
df <- tibble(
  x = runif(5),
  y = rnorm(5)
)

# output is vector
df$x
df[["x"]]

# output is still tibble
df["x"]
```


# 11 Data import

## general use
* you can skip the meta dataline in the first `n` rows/lines with `skip = n`
* you can handle the data without column names using `colnames = FALSE`
* you can use `na = "<sth>"` to specifies the value that are used to represnt missing value in your file, this case <sth>

## comparison with base R
* faster
* does not convert character to vectors and so on...

## excersize 2
```{r}
# 2
union(names(formals(read_csv)), names(formals(read_tsv)))
```

## excersize 4
```{r}
x <- "x,y\n1,'a,b'"
read_delim(x, ",", quote = "'")
read_csv(x)
```


## eccersize 5
```{r}
read_csv("a,b\n1,2,3\n4,5,6")

read_csv("a,b,c\n1,2\n1,2,3,4")

read_csv("a,b\n\"1")

read_csv("a,b\n1,2\na,b")

read_csv("a;b\n1;3")
read_csv2("a;b\n1;3") # this works
```

## 11.3 parsing a vector
```{r}
parse_integer(c("1", "2", "3"))
```

```{r}
x  <- parse_integer(c("1", "abc", "123.45", "."), na = ".")
# if you get warn, the failues would be missing in the output
x
# see problems
problems(x)
```

#### examples of parse
```{r}
parse_number("It cost $123.45")
```


```{r}
charToRaw("Hadley")
```


#### the problem with encoding
```{r}
x1 <- "El Ni\xf1o was particularly bad this year" # Latin1 style
x2 <- "\x82\xb1\x82\xf1\x82\xc9\x82\xbf\x82\xcd" # shift-jis style

parse_character(x1, locale = locale(encoding = "Latin1"))
parse_character(x2, locale = locale(encoding = "Shift-JIS"))

# you can "guess" the encoding
guess_encoding(charToRaw(x1))
```


```{r}

fruit <- c("apple", "banana")
parse_factor(c("apple", "banana", "bananana"), levels = fruit)
```


### date and time
```{r}
parse_datetime("2010-10-01T2010")
parse_datetime("20101010")

```


```{r}
parse_date("2010-10-01")
parse_date("2010/10/01")

```



```{r}
library(hms)
parse_time("01:10 am")
parse_time("20:10:01")
```

```{r}
parse_date("01/02/15", "%m/%d/%y")

parse_date("01/02/15", "%d/%m/%y")

parse_date("01/02/15", "%y/%m/%d")

parse_time("01/15/30", "%H/%M/%OS")

```


### 11.3.5 Excercize 
```{r}
# 2

locale(decimal_mark = ".", grouping_mark = ".")
```

