---
title: '3'
output: html_document
---

```{r, message=FALSE}
rm(list = ls())
library(tidyverse)
```

### 3.2.2 Creating ggplot
```{r}
ggplot(data  = mpg ) + geom_point(mapping = aes(x = displ, y = hwy))
# seems same
ggplot(data  = mpg, aes(x = displ, y = hwy) ) + geom_point()
```


### 3.2.3
### template
```{r}
######################################################################
# ggplot(data = <DATA>) + <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>)) #
######################################################################
# put data in <DATA>
# put function (geom_point etc) in <GEOM_FUNCTION>
# put variables to plot in <MAPPINGS>
```

### 3.2.4 Exercises
### scatter plot of class vs drv
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = class, y = drv))
```

## 3.3
```{r}
ggplot(data  = mpg ) + geom_point(mapping = aes(x = displ, y = hwy, color = class))
```
* change the color of the points


```{r}
ggplot(data  = mpg ) + geom_point(mapping = aes(x = displ, y = hwy, size = class))
```
### you will get a warning here
* `size = ` will change the size of the points
* using `size = ` for discrete data is not a good idea

```{r}
ggplot(data  = mpg ) + geom_point(mapping = aes(x = displ, y = hwy, alpha = class))
```
* change the shade of the points (black-white)



```{r}
ggplot(data  = mpg ) + geom_point(mapping = aes(x = displ, y = hwy, shape = class))
```
* change the shape of the points
* additional groups will go unplotted when you use the shape aesthetic and
* the number of class exceed the default number of shapes (6)

```{r}
ggplot(data  = mpg ) + geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```
* change the color of all plots
* note that `color = ` is outisude `aes( )`

### 3.3.1 Exercises
### 3
```{r}
ggplot(data  = mpg ) + geom_point(mapping = aes(x = displ, y = hwy, color = cyl))
```
* you can use color or size, but not shape for continuous variables

### 5
```{r}
ggplot(data  = mpg ) + geom_point(mapping = aes(x = displ, y = hwy, stroke = 6))
```
* Stroke changes the color of the border for shapes (22-24).

### 6
```{r}
ggplot(data  = mpg ) + geom_point(mapping = aes(x = displ, y = hwy, color = displ < 5))
```

* In this case, it is logical variable which is TRUE or FALSE
* This also explains exercise 1, color = "blue" created a categorical variable\
* 	that only had one category: “blue”.

## 3.5
* split your plot into facets, subplots that each desplay one subset of the dataset
```{r}
ggplot(data = mpg) + 
	geom_point(mapping = aes(x = displ, y = hwy)) +
	facet_wrap(~ class, nrow = 2)
```
* The variable that you pass to facet_wrap() should be discrete.

```{r}
ggplot(data = mpg) + 
	geom_point(mapping = aes(x = displ, y = hwy)) +
	facet_wrap(~ class, nrow = 3)
```

```{r}
ggplot(data = mpg) + 
	geom_point(mapping = aes(x = displ, y = hwy)) +
	facet_grid(drv ~ cyl)
```
* facet your plot on the combination of the two variables
* ex) the plot above show the plot of x and y for each pair (drv, cyl)

```{r}
ggplot(data = mpg) + 
	geom_point(mapping = aes(x = displ, y = hwy)) +
	facet_grid(drv ~ .)
```
* devide baed on one variable by row = plot drv on the y-axis

```{r}
ggplot(data = mpg) + 
	geom_point(mapping = aes(x = displ, y = hwy)) +
	facet_grid(. ~ drv)
```
* devide baed on one variable by column = plot drv on the x-axis

## 3.6
```{r}
ggplot(data = mpg) + 
	geom_smooth(mapping = aes(x = displ, y = hwy))
ggplot(data = mpg) + 
	geom_smooth(mapping = aes(x = displ, y = hwy, linetype = drv))
```
* separates the cars into three lines based on their drv value with different linetype each


```{r}
ggplot(data = mpg) + 
	geom_smooth(mapping = aes(x = displ, y = hwy, group = drv))
```
* separates the cars into three lines based on their drv value with same linetype each

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
	geom_smooth() + 
	geom_point(mapping = aes(color = class))
```
* points are separeted by the color based on class

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
	geom_smooth(data = filter(mpg, class == "subcompact"), se = FALSE) + 
	geom_point(mapping = aes(color = class))
```
* the local data argument in `geom_smooth()` (= `filter(mpg, class == "subcompact")`)
* overrides the global data in argument ggplot() for that layer only
* smooth line is drawn for the data with class == "subcompact"


### 3.6.1 Exercises
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```
* separate both the smooth line and points with different colors based on `color = drv`

### 3: `show.legend = FALSE` should be included in geom_point, geom_smooth, etc
* you need `theme(lengend = "none")

### 6
* top left
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth(color = "blue", se = FALSE)

ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth(color = "red", se = FALSE)
```

* top right
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth(color = "blue", se = FALSE, aes(group = drv))
```

* mid left
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```

* mid right
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(mapping = aes(color = drv)) + 
  geom_smooth(se = FALSE)

# incorrect version
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = FALSE, data = filter(mpg, drv == "r"))
```

* bottom left
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(mapping = aes(color = drv)) + 
  geom_smooth(se = FALSE, mapping = aes(linetype = drv))
```

* bottom right
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, fill = drv)) + 
  geom_point(color = "white", shape = 21)

# better?
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, fill = drv)) + 
  geom_point(color = "white", shape = 21, size = 4)
```

## 3.7
```{r}
# the two plots below are same
ggplot(data = diamonds, aes(x = cut)) + stat_count()
ggplot(data = diamonds, aes(x = cut)) + geom_bar()
```

```{r}
demo <- tribble(
  ~a,      ~b,
  "bar_1", 20,
  "bar_2", 30,
  "bar_3", 40
)

#ggplot(demo, aes(x = a, y = b)) + geom_bar() # this does not work
ggplot(demo, aes(x = a, y = b)) + geom_bar(stat = "identity")
# stacked bar plot
# 積み重ねる型のバープロット
```

```{r}
ggplot(data = diamonds) + 
	stat_summary(
		mapping = aes(x = cut, y = depth),
		fun.ymin = min,
		fun.ymax = max,
		fun.y = median
		)
```

* the output is a point for each `cut` with bar length for minimum and maximum
```{r}
ggplot(data = diamonds) + 
  geom_pointrange(
    mapping = aes(x = cut, y = depth),
    stat = "summary",
    fun.ymin = min,
    fun.ymax = max,
    fun.y = mean # you can use median instead of mean
  	)
```

### 3.7.1
### 2
```{r}
ggplot(data = diamonds, aes(x = cut, y = depth)) + geom_col()
# the default for geom_col: identity
# the default for geom_bar: summary
```

### 4
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
	stat_smooth() 
```

### 5
```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, y = ..prop..))
# this does not give what we want

ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, y = ..prop.., group = 1))
# this works
# if `group` is not set to 1 or whatever, all the bars have prop == 1
# group="whatever" is a "dummy" grouping to override the default behavior
# for detail, see here -> http://stackoverflow.com/questions/39878813/r-ggplot-geom-bar-meaning-of-aesgroup-1

ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, y = ..prop.., fill = color, group = color))
# this works too
```

## 3.8 Position adjustment
```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, color = cut))
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, fill = cut))
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, group = cut)) # same as without `group = `

ggplot(data = diamonds, mapping = aes(x = cut, color = clarity)) + 
  geom_bar(fill = NA, position = "identity")
ggplot(data = diamonds, mapping = aes(x = cut, fill = clarity)) + 
  geom_bar(alpha = .2, position = "identity")
```

* it place each object exactly where it falls in the context of the plot
* in the case above, each bar starst from zero, and thus overlaps 
* それぞれのclarity毎に、ゼロから積み上げるbarを作るから、全てのbarが重なっている
* alphaで薄さを管理、fill=NAの方は枠だけ中は空白


```{r}
ggplot(data = diamonds, mapping = aes(x = cut, fill = clarity)) + 
  geom_bar(position = "fill")
```
* each set of stacked bar the same height
* hence easy to compare the proportions across group (across differnet sets of `cut`)
* 各barの高さは等しい、縦軸は割合なので、`cut`毎にclarityの割合を比べやすい

```{r}
ggplot(data = diamonds, mapping = aes(x = cut, color = clarity)) + 
  geom_bar(position = "fill")
```
*見にくい

```{r}
ggplot(data = diamonds, mapping = aes(x = cut, fill = clarity)) + 
  geom_bar(position = "dodge")
```
* places overlapping objects directly beside one another
* This makes it easier to compare individual values.
* identiyを使うと重なってしまう棒を隣り合わせて並べていくので、被るところがない
* 縦軸は割合ではなく、積み重ねたカウント

```{r}
# "jitter" add random noise to each point
ggplot(data  = mpg ) + geom_point(mapping = aes(x = displ, y = hwy), position = "jitter")
```
* deal with overplotting, 同じ値を重ねてしまう問題


### 3.8.1 Excercises
### 1
* both cty and bwy is discrete and thus oveplotting occurs
# adding jitter does not necessarily make sense because this manipulation will change information
```{r}
ggplot(data  = mpg ) + geom_point(mapping = aes(x = cty, y = hwy), position = "jitter")
ggplot(data  = mpg ) + geom_point(mapping = aes(x = cty, y = hwy))
```

### 2
* `width` and `height` to control the amount of jitter
* vertical jitter for `width` and horizontal jitter for `height`

```{r}
ggplot(data  = mpg, mapping = aes(x = cty, y = hwy) ) + geom_jitter()
```

```{r}
ggplot(data  = mpg, mapping = aes(x = cty, y = hwy) ) + geom_jitter(width = 20, height = 20)
```
* too much noise

### 3
* geom_count will change the size of points based on the observation each
# そのポイントに落ちるデータポイントの数に基づいてプロットのサイズが変わる
```{r}
ggplot(data  = mpg, mapping = aes(x = cty, y = hwy) ) + geom_jitter()
ggplot(data  = mpg, mapping = aes(x = cty, y = hwy) ) + geom_count()
```

### 4
```{r}
ggplot(data = mpg, aes(x = drv, y = hwy, color = class)) +
  geom_boxplot()

ggplot(data = mpg, aes(x = drv, y = hwy, color = class)) +
  geom_boxplot(position = "identity") # convey little information because of overlaps

ggplot(data = mpg, aes(x = drv, y = hwy, fill = class)) +
  geom_boxplot()
# compare the figures above
```

## 3.9 Coordinate systems
```{r}
ggplot(data = mpg, aes(x = drv, y = hwy, fill = class)) +
  geom_boxplot() +
  coord_flip()
# switch the x and y axes

ggplot(data = mpg, aes(x = drv, y = hwy, color = class)) +
  geom_boxplot() +
  coord_flip()

ggplot(data = mpg, aes(x = drv, color = class)) +
  geom_bar()
ggplot(data = mpg, aes(x = drv, group = class)) +
  geom_bar()
```

* coord_quickmap
* The group aesthetic determines which cases are connected together into a polygon
```{r}
library(maps)
nz <- map_data("nz")

ggplot(nz, aes(x = long, y = lat, group = group)) + 
  geom_polygon(fill = "white", color = "black")
```


```{r}
bar <- ggplot(data = diamonds) + 
  geom_bar(
    mapping = aes(x = cut, fill = cut), 
    show.legend = FALSE, 
    width = 1 
  ) + 
  theme(aspect.ratio = 1) + # `aspect.ratio` determines ratio of vartical and horizontal
  labs(x = NULL, y = NULL)

bar <- bar + coord_polar()
```

### 3.9.1
### 1
```{r}
ggplot(mpg, aes(x = drv, fill = class)) +
  geom_bar() +
  coord_polar()

ggplot(mpg, aes(x = drv, fill = class)) +
  geom_bar() +
  coord_polar(theta = "y")

# answer?
ggplot(mpg, aes(x = factor(1), fill = class)) +
  geom_bar()　# カウントとして出力される

ggplot(mpg, aes(x = factor(1), fill = class)) +
  geom_bar(positon = "fill") # 割合として出力される

ggplot(mpg, aes(x = drv, fill = class)) + 
  geom_bar(position = "fill") +
  coord_polar()

ggplot(mpg, aes(x = drv, fill = class)) + 
  geom_bar(position = "fill") +
  coord_polar(theta = "y")
# theta = "y" will give you the variable in `x =` in y axis 
# theta = "x" will give you the variable in `x =` in x axis
```

### 3
```{r}
ggplot(nz, aes(x = long, y = lat, group = group)) + 
  geom_polygon() +
  coord_quickmap() # if you add this, the shape slightly changes

ggplot(nz, aes(x = long, y = lat, group = group)) + 
  geom_polygon() +
  coord_map() # if you add this, the shape slightly changes
```

### 4
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() +
  geom_abline() +# y = x degree angle line
  coord_fixed() # ensure that the abline is at a 45 degree angle
```